\thistype{UnivariateMonomial}
\History{Manuel Bronstein}{20/5/94}{created}
\Usage{import from \this~R\\ import from \this(R, x)}
\Params{
{\em R} & \altype{ExpressionType} & Coefficients of the monomials\\
        & \altype{ArithmeticType} &\\
{\em x} & \altype{Symbol} & The variable name (optional)\\
}
\Descr{This type implements univariate monomials with coefficients in R.}
\begin{exports}
%\category{\altype{Order}}\\
\category{\altype{ExpressionType}}\\
\alexp{apply}: & (\%, TREE) $\to$ TREE & Applies a monomial to a tree\\
\alexp{coefficient}: & \% $\to$ R & Extraction of the coefficient\\
\alexp{degree}: & \% $\to$ \altype{Integer} & The degree of a monomial\\
\alexp{map}: & (R $\to$ R) $\to$ \% $\to$ \% & Lift a map\\
\alexp{map!}: & (R $\to$ R) $\to$ \% $\to$ \% & Lift a map\\
\alexp{monomial}: & (R, \altype{Integer}) $\to$ \% & Creation of a monomial\\
\alexp{setCoefficient!}:
& (\%, R) $\to$ R & In--place coefficient modification\\
\alexp{setDegree!}: & (\%, Z) $\to$ Z & In-place degree modification\\
\end{exports}
\begin{exports}[if $R$ has \altype{FiniteCharacteristic} then]
\alexp{pthPower}: & \% $\to$ \% & Exponentiation to the characteristic\\
\alexp{pthPower!}:
& \% $\to$ \% & In--place exponentiation to the characteristic\\
\end{exports}
\begin{aswhere}
TREE &==& \altype{ExpressionTree}\\
\end{aswhere}
\alpage{apply}
\Usage{\name(p, t)}
\Signature{(\%, \altype{ExpressionTree})}{\altype{ExpressionTree}}
\Params{
{\em p} & \% & A monomial\\
{\em t} & \altype{ExpressionTree} & An expression tree\\
}
\Retval{Returns p as an expression tree using t as root variable name.}
\alpage{coefficient}
\Usage{\name~p}
\Signature{\%}{R}
\Params{ {\em p} & \% & A monomial\\ }
\Retval{Returns the coefficient of $p$, \ie $c$ where $p = c\; x^n$.}
\alseealso{\alexp{degree}, \alexp{setCoefficient!}}
\alpage{degree}
\Usage{\name~p}
\Signature{\%}{\altype{Integer}}
\Params{ {\em p} & \% & A monomial\\ }
\Retval{Returns the degree of $p$, \ie $n$ where $p = c\; x^n$.}
\alseealso{\alexp{coefficient}}
\alpage{map}
\altarget{\name!}
\Usage{\name~f\\\name!~f\\\name(f)(p)\\\name!(f)(p)}
\Signature{(R $\to$ R) $\to$ \%}{\%}
\Params{
{\em f} & R $\to$ R & A map\\
{\em p} & \% & A monomial\\
}
\Descr{\name(f)(p) returns $f(a) x^n$ where $p = a x^n$,
while \name(f) returns the mapping $p \to f(p)$.
In both cases, \name!~does not make a copy of $p$ but modifies it in place.}
\alpage{monomial}
\Usage{\name(c, n)}
\Signature{(R, \altype{Integer})}{\%}
\Params{
{\em c} & R & A scalar\\
{\em n} & \altype{Integer} & An exponent\\
}
\Retval{Returns the monomial $c\; x^n$.}
\alpage{pthPower}
\altarget{\name!}
\Usage{ \name~p\\ \name!~p }
\Signature{\%}{\%}
\Params{ {\em p} & \% & A monomial\\ }
\Retval{Returns $p^{\mbox{characteristic}}$.}
\Remarks{\name!~does not make a copy of $p$, which is therefore
modified after the call. It is unsafe to use the variable $p$
after the call, unless it has been assigned to the result
of the call, as in {\tt p := pthPower!~p}.}
\alpage{setCoefficient!}
\Usage{\name(p, c)}
\Signature{(\%, R)}{R}
\Params{
{\em p} & \% & A monomial\\
{\em c} & R & A scalar\\
}
\Descr{Sets the coefficient of $p$ to $c$,\ie changes $p = d\; x^n$ into
$c\; x^n$}
\Retval{Returns the new coefficient $c$.}
\alseealso{\alexp{coefficient}}
\alpage{setDegree!}
\Usage{\name(p, c)}
\Signature{(\%, \altype{Integer})}{\altype{Integer}}
\Params{
{\em p} & \% & A monomial\\
{\em n} & \altype{Integer} & An exponent\\
}
\Descr{Sets the degree of $p$ to $n$,\ie changes $p = c\; x^m$ into
$c\; x^n$}
\Retval{Returns the new degree $n$.}
\alseealso{\alexp{degree}}
